\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Hypothesis Testing on Superstore Data}
\author{Karun Ram}

\begin{document}
\maketitle
\section{Introduction} 
This short statistical analysis attempts to explain some of the justification behind the features selected for the neural network I built. I attempt to consider features that affect the shipping time of an order. A high level of significance ($\alpha$) is used to account for the relative homogeneity of the data.
\newpage
\section{Shipping Times Across Categories} 
\hrulefill \\
Hypotheses: \\
$H_0$: The shipping time is equal across product categories.\\
$H_A$: The shipping time is not equal across product categories. \\

To test this, we consider the following distribution (extracted from the data using the code in Stats.py):
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 Category & Observed Shipping Time (days)& Expected Shipping Time (days) \\ 
\hline
\hline
Bookcases & 3.811 & 3.958\\
Chairs & 3.900 & 3.958\\
Labels & 4.003 & 3.958\\
Tables & 3.893 & 3.958\\
Storage & 3.975 & 3.958\\
Furnishings & 3.961 & 3.958\\
Art & 4.054 & 3.958\\
Phones & 4.001 & 3.958\\
Binders & 4.022 & 3.958\\
Appliances & 3.989 & 3.958\\
Paper & 3.888 & 3.958\\
Accessories & 3.886 & 3.958\\
Envelopes & 4.016 & 3.958\\
Fasteners & 3.977 & 3.958\\
Supplies & 4.016 & 3.958\\
Machines & 3.748 & 3.958\\
Copiers & 3.618 & 3.958\\
 \hline
\end{tabular}
\end{center}
\hfill \\
Given this data, we can perform a chi-squared test for goodness of fit with $df=16$ with $\alpha=0.20$. Using the distribution above, we obtain $\chi^2_{df=16}=0.05672$. \\

Since $P(\chi^2 > 0.05672) \approx 1 > \alpha$, we fail to reject $H_0$ and conclude that the assumption equal shipping time across product categories cannot be rejected.
\newpage
\section{Shipping Times Across Regions}
\hrulefill \\
Hypotheses:\\
$H_0$: The shipping time is equal across regions.\\
$H_A$: The shipping time is not equal across regions. \\

To test this, we consider the following distribution (extracted from the data using the code in Stats.py):
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 Region & Observed Shipping Time (days)& Expected Shipping Time (days) \\ 
\hline
\hline
South & 3.958 & 3.958\\
West & 3.93 & 3.958\\
Central & 4.058 & 3.958\\
East & 3.909 & 3.958\\
 \hline
\end{tabular}
\end{center}
\hfill \\
Given this data, we can perform a chi-squared test for goodness of fit with $df=3$ with $\alpha=0.20$. Using the distribution above, we obtain $\chi^2_{df=3}=0.00333$. \\

Since $P(\chi^2 > 0.00333) \approx 0.999 > \alpha$, we fail to reject $H_0$ and conclude that the assumption of equal shipping time across regions cannot be rejected.
\newpage

\section{Shipping Times Across Shipping Modes}
\hrulefill \\
Hypotheses:\\
$H_0$: The shipping time is equal across shipping modes.\\
$H_A$: The shipping time is not equal across shipping modes. \\

To test this, we consider the following distribution (extracted from the data using the code in Stats.py):
\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
Shipping Mode & Observed Shipping Time (days)& Expected Shipping Time (days) \\ 
\hline
\hline
Second Class & 3.238 & 3.958\\
Standard Class & 5.007 & 3.958\\
First Class & 2.183 & 3.958\\
Same Day & 0.044 & 3.958\\
 \hline
\end{tabular}
\end{center}
\hfill \\
Given this data, we can perform a chi-squared test for goodness of fit with $df=3$ with $\alpha=0.20$. Using the distribution above, we obtain $\chi^2_{df=3}=5.0754$. \\

Since $P(\chi^2 > 5.0754) \approx 0.1664 < \alpha$, we reject $H_0$ and conclude that the assumption of equal shipping time across shipping modes can be rejected. This, intuitively, is reasonable since shipping modes directly impact shipping speed.
\end{document}  